Teams analyses

### 2022-04-19 scripts/r/teams-analyses.Rmd
✨ - prepare files with analytic questionnaire responses

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(magrittr)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(magrittr)
library(glue)
```

@@

```{r}
dir.create("data/questionnaires/msa_data_analysis_files/", showWarnings = FALSE)

n_teams <- nrow(teams_analyses)

for (team in 1:n_teams) {
  animal <- teams_analyses$Q17[team]
  file_name <- as.character(glue("data/questionnaires/msa_data_analysis_files/{animal}.txt"))

  txt <- ""

  for (q in 4:15) {
    txt <- paste(
      txt,
      full_q_text[1,q], "\n",
      teams_analyses[team,q],
      "\n\n",
      "------------------------------------------------------------------------"
      , "\n\n",
      sep = "\n"
    )
  }

  write_file(txt, file_name)
}
```
